---
title: "Thermal Gradient Analyses"
author: "Laura Segura Hernández"
date: "1/17/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```

# Libraries
```{r, message=FALSE}
library(googlesheets4)
library(tidyr)
library(dplyr)
library(data.table)
library(lubridate)
library(NRES803)
library(ggplot2)
library(lme4)
library(DHARMa)
library(forcats)
library(gap)
```

# Signing up to my google account and getting the data sheet

I just need to run this line to give access to my google account to tidy verse to be able to work on the google sheet more easily

```{r, message=FALSE}
gs4_auth(email=TRUE)
```


Now I can read the ones I need:
```{r}

# Getting the behavior data
df<-read_sheet('https://docs.google.com/spreadsheets/d/1P7omRunnlCTOQz2YM8-oaBCRXCbVdOQ3CjWfBQ2ldrM/edit#gid=0', sheet="Raw data", na = c("", "NA","NULL", NULL))

df[is.null(df)]<-NA

df<-as.data.frame(df)
df<- df %>% 
  mutate(Zone=factor(Zone, levels=c("1","2", "3", "4","5","6", "7", "8", "9", "10", "11", "12", "13","End", "Non visible"))) %>%
  rename(trial=Trial, totalduration= `Duration secs`, lane=Lane, stage=Stage, zone=Zone, enter=Enter, time=`Time spent secs`, priorexpdur=`Prior exploration duration`, priorexpmin=`Prior exploration min`, priorexpmax=`Prior exploration max`)


#Getting the temperature data

temps<-range_read('https://docs.google.com/spreadsheets/d/1P7omRunnlCTOQz2YM8-oaBCRXCbVdOQ3CjWfBQ2ldrM/edit#gid=0', sheet="Temperatures", na = c("", "NA","NULL", NULL))

temps[is.null(df)]<-NA

as.data.frame(temps)


```

# Organizing the temperature data
```{r}

temps<-temps %>%
  select(-c("Channel 2", "Channel 9" ,"Channel 16")) %>%
  mutate(Zone=as.factor(Zone)) %>%
  rename(trial=Trial, meantemptrial=Trialaverage, zonegradient=Zonegradient, zone=Zone)

# Getting overall average of the temperature gradient across all trials
tempsb<- temps %>%
  group_by(zonegradient) %>%
  summarize(meantempall=mean(meantemptrial),
            setempall=sd(meantemptrial)/11)

# Adding that overall average to the temperatures of each trial
temps<-temps %>%
  full_join(tempsb, by="zonegradient")

# Separating temperatures per trial
temps1<-temps %>% filter(trial==1)
temps2<-temps %>% filter(trial==2)
temps3<-temps %>% filter(trial==3)
temps4<-temps %>% filter(trial==4)
temps5<-temps %>% filter(trial==5)
temps6<-temps %>% filter(trial==6)
temps7<-temps %>% filter(trial==7)
temps8<-temps %>% filter(trial==8)
temps9<-temps %>% filter(trial==9)
temps10<-temps %>% filter(trial==10)
temps11<-temps %>% filter(trial==11)



```

# Organizing the behavioral data

## Merging temperatures to each trial
```{r}
# Trial 1
df1<- df %>%
  filter(trial==1) %>%
  full_join(temps1, by="zone")

# Trial2
df2<- df %>%
  filter(trial==2) %>%
  full_join(temps2, by="zone")

# Trial 3
df3<- df %>%
  filter(trial==3) %>%
  full_join(temps3, by="zone")

# Trial 4
df4<- df %>%
  filter(trial==4) %>%
  full_join(temps4, by="zone")

# Trial 5
df5<- df %>%
  filter(trial==5) %>%
  full_join(temps5, by="zone")

# Trial 6
df6<- df %>%
  filter(trial==6) %>%
  full_join(temps6, by="zone")

# Trial 7
df7<- df %>%
  filter(trial==7) %>%
  full_join(temps7, by="zone")

# Trial 8
df8<- df %>%
  filter(trial==8) %>%
  full_join(temps8, by="zone")

# Trial 9
df9<- df %>%
  filter(trial==9) %>%
  full_join(temps9, by="zone")

# Trial 10
df10<- df %>%
  filter(trial==10) %>%
  full_join(temps10, by="zone")

# Trial 11
df11<- df %>%
  filter(trial==11) %>%
  full_join(temps11, by="zone")


```

# Merging all files together
```{r}
beh<-rbind(df1,df2,df3,df4,df5,df6,df7,df8,df9,df10,df11)

beh<-beh %>% 
  filter(zone!="End") %>%
  mutate(proptime=time/totalduration)

beh$stage <- fct_relevel(beh$stage, "Protonymph", "Deutonymph", "Tritonymph",  "Male", "Female")
levels(beh$stage) # new col is not attached so must use data$

# Colors
colors<-c("#ff7f00", "#e41a1c", "#a65628",  "#984ea3", "#377eb8")

```

# Plotting

## Comparing temperatures across trials

```{r}
d<-data.frame(zonegradient = c(1,13), meantemptrial = c(20,40))

temps$upr<-temps$meantempall+temps$setempall
temps$lwr<-temps$meantempall-temps$setempall

ggplot() +
  geom_line(temps, mapping=aes(x=zonegradient, y=meantemptrial, color=as.factor(trial)), size=0.7)+
  geom_point(temps,mapping=aes(x=zonegradient,y=meantemptrial, color=as.factor(trial)), size=2, alpha=0.5)+
  geom_line(temps, mapping=aes(x=zonegradient, y=meantempall), color="black", size=0.5)+
  geom_ribbon(data=temps, mapping=aes(ymin = lwr, ymax = upr,x=zonegradient, y=meantempall), alpha = 0.7, color="black")+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"))+
  labs(color="Trial")+ylab("Temperature (Celsius)")+xlab("Zone")+
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8,9,10,11,12,13))+ 
  geom_line(data = d, mapping =aes(x = zonegradient, y = meantemptrial), colour = "red", size=1.5, linetype="dashed")

ggsave(plot=last_plot(),filename="Temperature_trials.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")


ggplot() +
  #geom_line(temps, mapping=aes(x=zonegradient, y=meantempall), color="black", size=1.5)+
  geom_ribbon(data=temps, mapping=aes(ymin = lwr, ymax = upr, x=zonegradient, y=meantempall), alpha = 0.5, color="black")
  #theme_classic()+
  #theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"))+
  #labs(color="Trial")+ylab("Temperature (Celsius)")+xlab("Zone")+
  #scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8,9,10,11,12,13))+ 
  #geom_line(data = d, mapping =aes(x = zonegradient, y = meantemptrial), colour = "red", size=1.5, linetype="dashed")

  
```



## Total time spent on each temperature zone 

### Accumulated time per ID and stage 

#### Data prep

```{r}
#Protonymphs
protos<-beh %>% filter(stage=="Protonymph") 

protos2<-protos%>%
  group_by(ID, meantemptrial, zone, trial.x) %>%
  summarize(time=sum(time), proptime=sum(proptime))

#Deutonymphs
deutos<-beh %>% filter(stage=="Deutonymph")

deutos2<-deutos%>%
  group_by(ID, meantemptrial, zone, trial.x) %>%
  summarize(time=sum(time), proptime=sum(proptime))

#Tritonymphs
tritos<-beh %>% filter(stage=="Tritonymph")

tritos2<-tritos%>%
  group_by(ID, meantemptrial, zone, trial.x) %>%
  summarize(time=sum(time), proptime=sum(proptime))

#Males
males<-beh %>% filter(stage=="Male")

males2<-males%>%
  group_by(ID, meantemptrial, zone, trial.x) %>%
  summarize(time=sum(time), proptime=sum(proptime))

#Females
females<-beh %>% filter(stage=="Female")

females2<-females%>%
  group_by(ID, meantemptrial, zone, trial.x) %>%
  summarize(time=sum(time), proptime=sum(proptime))


```

#### Plots: total time

```{r}
# To add the ID labels to the grid, remove the "strip.text.x = element_blank()" for in the code line: 
#theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"),legend.position="none")+


## Protonymphs
ggplot(protos2, aes(x=meantemptrial, y=time, fill=as.factor(trial.x))) +geom_bar(stat="identity", width=1) + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)),panel.spacing = unit(7, "mm"))+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Protonymphs by ID")+
  labs(fill="Trial")+ 
  facet_wrap(vars(ID), scales="fixed")

ggsave(plot=last_plot(),filename="Acummtime_ind_trial_Protos.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")


## Deutonymphs
ggplot(deutos2, aes(x=meantemptrial, y=time, fill=as.factor(trial.x))) +geom_bar(stat="identity", width=1) + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)),panel.spacing = unit(7, "mm"))+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Deutonymphs by ID")+
  labs(fill="Trial")+ 
  facet_wrap(vars(ID), scales="fixed")

ggsave(plot=last_plot(),filename="Acummtime_ind_trial_Deutos.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")


## Tritonymphs

### By individual
ggplot(tritos2, aes(x=meantemptrial, y=time, fill=as.factor(trial.x))) +geom_bar(stat="identity", width=1) + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)),panel.spacing = unit(7, "mm"))+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Tritonymphs by ID")+
  labs(fill="Trial")+ 
  facet_wrap(vars(ID), scales="fixed")

ggsave(plot=last_plot(),filename="Acummtime_ind_trial_tritos.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")


## Males

### By individual
ggplot(males2, aes(x=meantemptrial, y=time, fill=as.factor(trial.x))) +geom_bar(stat="identity", width=1) + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)),panel.spacing = unit(7, "mm"))+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Males by ID")+
  labs(fill="Trial")+ 
  facet_wrap(vars(ID), scales="fixed")
ggsave(plot=last_plot(),filename="Acummtime_ind_trial_males.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")


## Females
ggplot(females2, aes(x=meantemptrial, y=time, fill=as.factor(trial.x))) +geom_bar(stat="identity", width=1) + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)),panel.spacing = unit(7, "mm"))+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Females by ID")+
  labs(fill="Trial")+ 
  facet_wrap(vars(ID), scales="fixed")

ggsave(plot=last_plot(),filename="Acummtime_ind_trial_females.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")



```

#### Plots: proportional time

```{r}

## Protonymphs

ggplot(protos2, aes(x=meantemptrial, y=proptime, fill=as.factor(trial.x))) +geom_bar(stat="identity", width=1) + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)),panel.spacing = unit(7, "mm"))+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Protonymphs by ID")+
  labs(fill="Trial")+ 
  facet_wrap(vars(ID), scales="fixed")

ggsave(plot=last_plot(),filename="Acummtimeprop_ind_trial_Protos.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")



## Deutonymphs
ggplot(deutos2, aes(x=meantemptrial, y=proptime, fill=as.factor(trial.x))) +geom_bar(stat="identity", width=1) + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)),panel.spacing = unit(7, "mm"))+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Deutonymphs by ID")+
  labs(fill="Trial")+ 
  facet_wrap(vars(ID), scales="fixed")

ggsave(plot=last_plot(),filename="Acummtimeprop_ind_trial_Deutos.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")




## Tritonymphs
ggplot(tritos2, aes(x=meantemptrial, y=proptime, fill=as.factor(trial.x))) +geom_bar(stat="identity", width=1) + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)),panel.spacing = unit(7, "mm"))+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Tritonymphs by ID")+
  labs(fill="Trial")+ 
  facet_wrap(vars(ID), scales="fixed")

ggsave(plot=last_plot(),filename="Acummtimeprop_ind_trial_tritos.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")





## Males
ggplot(males2, aes(x=meantemptrial, y=proptime, fill=as.factor(trial.x))) +geom_bar(stat="identity", width=1) + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)),panel.spacing = unit(7, "mm"))+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Males by ID")+
  labs(fill="Trial")+ 
  facet_wrap(vars(ID), scales="fixed")

ggsave(plot=last_plot(),filename="Acummtimeprop_ind_trial_males.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")




## Females
ggplot(females2, aes(x=meantemptrial, y=proptime, fill=as.factor(trial.x))) +geom_bar(stat="identity", width=1) + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)),panel.spacing = unit(7, "mm"))+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Females by ID")+
  labs(fill="Trial")+ 
  facet_wrap(vars(ID), scales="fixed")

ggsave(plot=last_plot(),filename="Acummtimeprop_ind_trial_females.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")


```



### Accumulated total time

#### Data prep

```{r}
### Protonymphs
protos3<-protos%>%
  group_by(meantempall, zone) %>%
  summarize(time=sum(time), proptime=sum(proptime))

### Deutonymphs
deutos3<-deutos%>%
  group_by(meantempall, zone) %>%
  summarize(time=sum(time), proptime=sum(proptime))


### Tritonymphs
tritos3<-tritos%>%
  group_by(meantempall, zone) %>%
  summarize(time=sum(time), proptime=sum(proptime))


### Males
males3<-males%>%
  group_by(meantempall, zone) %>%
  summarize(time=sum(time), proptime=sum(proptime))


### Females
females3<-females%>%
  group_by(meantempall, zone) %>%
  summarize(time=sum(time), proptime=sum(proptime))


```


#### Plots: Total time



```{r}
### Protonymphs
ggplot(protos3, aes(x=meantempall, y=time)) +geom_bar(stat="identity", fill="#ff7f00") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Protonymphs all together")

ggsave(plot=last_plot(),filename="Acummtime_trial_Protos.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")

### Deutonymphs
ggplot(deutos3, aes(x=meantempall, y=time)) +geom_bar(stat="identity", fill="#e41a1c") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Deutonymphs all together")

ggsave(plot=last_plot(),filename="Acummtime_trial_Deutos.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")

### Tritonymphs
ggplot(tritos3, aes(x=meantempall, y=time)) +geom_bar(stat="identity", fill="#a65628") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Tritonymphs all together")

ggsave(plot=last_plot(),filename="Acummtime_trial_tritos.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")

### Males
ggplot(males3, aes(x=meantempall, y=time)) +geom_bar(stat="identity", fill="#984ea3") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Males all together")

ggsave(plot=last_plot(),filename="Acummtime_trial_males.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")

### Females
ggplot(females3, aes(x=meantempall, y=time)) +geom_bar(stat="identity", fill="#377eb8") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Females all together")

ggsave(plot=last_plot(),filename="Acummtime_trial_females.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")


```


#### Plots: proportional accumulated time

```{r}
### Protonymphs
ggplot(protos3, aes(x=meantempall, y=proptime)) +geom_bar(stat="identity", fill="#ff7f00") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Accumulated proportional time")+ ggtitle("Protonymphs all together")

ggsave(plot=last_plot(),filename="Acummtimeprop_trial_Protos.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")

### Deutonymphs
ggplot(deutos3, aes(x=meantempall, y=proptime)) +geom_bar(stat="identity", fill="#e41a1c") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Accumulated proportional time")+ ggtitle("Deutonymphs all together")
ggsave(plot=last_plot(),filename="Acummtimeprop_trial_Deutos.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")


### Tritonymphs
ggplot(tritos3, aes(x=meantempall, y=proptime)) +geom_bar(stat="identity", fill="#a65628") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Accumulated proportional time")+ ggtitle("Tritonymphs all together")

ggsave(plot=last_plot(),filename="Acummtimeprop_trial_tritos.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")


### Males
ggplot(males3, aes(x=meantempall, y=proptime)) +geom_bar(stat="identity", fill="#984ea3") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Accumulated proportional time")+ ggtitle("Males all together")

ggsave(plot=last_plot(),filename="Acummtimeprop_trial_males.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")

### Females
ggplot(females3, aes(x=meantempall, y=proptime)) +geom_bar(stat="identity", fill="#377eb8") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Accumulated proportional time")+ ggtitle("Females all together")

ggsave(plot=last_plot(),filename="Acummtimeprop_trial_females.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")



```


## Average time spent

### Data prep
```{r}
### Protonymphs
protos3<-protos%>%
  group_by(meantempall, zone) %>%
  summarize(time=sum(time), proptime=sum(proptime))


behav<-beh%>%
  group_by(stage, ID, meantempall, zone) %>%
  summarize(avtime=mean(time))

behav3<-beh%>%
  group_by(stage, meantempall, zone) %>%
  summarize(avtime=mean(time), sdtime=sd(time)) %>%
  na.omit()


ggplot(behav3, aes(x=meantempall, y=avtime, fill=stage)) +geom_bar(stat="identity") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Mean time (s)")+ ggtitle("Mean time across all IDs")+
  scale_fill_manual(values=colors) + 
  geom_errorbar(aes(ymin=avtime, ymax=avtime+sdtime), width=.2,
                 position=position_dodge(.9)) +
  facet_wrap(vars(stage))

ggsave(plot=last_plot(),filename="Avtime_stages_sd.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")

ggplot(behav3, aes(x=meantempall, y=avtime, fill=stage)) +geom_bar(stat="identity") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Mean time (s)")+ ggtitle("Mean time across all IDs")+
  scale_fill_manual(values=colors) +
  facet_wrap(vars(stage))

ggsave(plot=last_plot(),filename="Avtime_stages.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")



```





## Per trial


```{r}
#Trial 2
t2<-beh %>% filter(trial.x==2)

t22<-t2%>%
  group_by(ID,stage, meantemptrial, zone) %>%
  summarize(time=sum(time), proptime=sum(proptime))

t23<-t2%>%
  group_by(stage,meantempall, zone) %>%
  summarize(time=sum(time), proptime=sum(proptime))

levels(t22$stage)
## Accumulated time

### By individual
ggplot(t22, aes(x=meantemptrial, y=time, fill=stage)) +geom_bar(stat="identity") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Trial 2 per ind")+
  scale_fill_manual(values=colors)+
  facet_wrap(vars(ID))

ggsave(plot=last_plot(),filename="Acummtime_ind_trial_2.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")


### Total among all individuals
ggplot(t23, aes(x=meantempall, y=time, fill=stage)) +geom_bar(stat="identity") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Trial 2")+
  scale_fill_manual(values=colors) +
  facet_wrap(vars(stage))

ggsave(plot=last_plot(),filename="Acummtime_trial_2.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")


## Accumulated proportional time

### By individual

ggplot(t22, aes(x=meantemptrial, y=proptime, fill=stage)) +geom_bar(stat="identity") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)), strip.text.x = element_blank(),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Trial 2 per ind")+
  scale_fill_manual(values=colors)+
  facet_wrap(vars(ID))

ggsave(plot=last_plot(),filename="Acummtimeprop_ind_trial_2.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")


### Total among all individuals
ggplot(t23, aes(x=meantempall, y=time, fill=stage)) +geom_bar(stat="identity") + 
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)),panel.spacing = unit(7, "mm"),legend.position="none")+
  xlab("Temperature (Celsius)")+  ylab("Accumulated time (s)")+ ggtitle("Trial 2")+
  scale_fill_manual(values=colors)
  facet_wrap(vars(stage))

ggsave(plot=last_plot(),filename="Acummtimeprop_trial_2.jpg",  path="Outputs/Exploratory plots/",width=7, height=7, units="in")


```





# Changing the order of Stage levels
```{r}
#df2$Stage <- fct_relevel(df2$Stage, "Protonymph", "Deutonymph", "Tritonymph", "Female", "Male")
#levels(df2$Stage) # new col is not attached so must use data$
```

